Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex

\noindent \underline{\em Proof of Statement (3).} We first prove that $\dcross_H(\bm{t}) \neq \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$. Set $r' = \gbot(\bm{t})$, and let $r$ be the full rectangle of $r'$. Define $h$ as the lowest segment crossing $r$ (note that $h$ definitely exists because otherwise $r$ has no trimmed rectangle). We will show $h \in \dcross_H(\bm{t})$, and hence $\dcross_H(\bm{t})$ cannot be empty. For this purpose, we need to prove that $h$ crosses both $B_{\bm{t}}$ and $r'$. However, $h$ crossing $r$ implies $h$ crossing $r'$, as has already been argued in our proof of statement (2). It thus remains to show that $h$ crosses $B_\bm{t}$.

@@

By the way $r'$ is defined, the bottom edge of $r'$ must be contained in $h$. Because $r' = \gbot(\bm{t})$, the bottom edge of $B_\bm{t}$ is contained in the bottom edge of $r'$ and hence also contained in $h$. This means that $h \cap B_{\bm{t}}\neq \emptyset$. On the other hand, the x-range of $h$ must contain that of $r'$ (because $h$ crosses $r'$), which in turn must contain that of $B_\bm{t}$ (because $r'$ covers $B_\bm{t}$). Thus, the x-range of $h$ covers that of $B_\bm{t}$. Combining this with $h \cap B_{\bm{t}}\neq \emptyset$ shows that $h$ must cross $B_\bm{t}$.

@@

A symmetric argument shows that $\dcross_V(\bm{t}) \ne \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$.

>>>>

\noindent \underline{\em Proof of Statement (3).} We first prove that $\dcross_H(\bm{t}) \neq \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$. Set $r' = \gbot(\bm{t})$, and let $r$ be the full rectangle of $r'$. Define $h$ as the lowest segment crossing $r$ (note that $h$ definitely exists because otherwise $r$ has no trimmed rectangle). We will show that $h \in \dcross_H(\bm{t})$, and hence $\dcross_H(\bm{t})$ cannot be empty. For this purpose, we should explain why $h$ crosses both $B_{\bm{t}}$ and $r'$. However, $h$ crossing $r$ implies $h$ crossing $r'$, as has already been argued in our proof of statement (2). It remains to show that $h$ crosses $B_\bm{t}$.

@@

By the way $r'$ is defined, the bottom edge of $r'$ must be contained in $h$. Because $r' = \gbot(\bm{t})$, the bottom edge of $B_\bm{t}$ is contained in the bottom edge of $r'$ and hence also contained in $h$. This means that $h \cap B_{\bm{t}}\neq \emptyset$. On the other hand, the x-range of $h$ must contain that of $r'$ (because $h$ crosses $r'$), which in turn must contain that of $B_\bm{t}$ (because $r'$ covers $B_\bm{t}$). Thus, the x-range of $h$ covers that of $B_\bm{t}$. Combining this with $h \cap B_{\bm{t}}\neq \emptyset$ yields that $h$ must cross $B_\bm{t}$.

@@

A symmetric argument assures us that $\dcross_V(\bm{t}) \ne \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$.
